---
title: "Mediterranean Swordfish"
output:
  rmdformats::html_clean:
    fig_width: 6
    fig_height: 6
    highlight: pygments
---


```{r knitr_init, echo=FALSE, results="asis", cache=FALSE}
library(knitr)

## Global options
options(max.print="75")
opts_chunk$set(fig.path="out/",
               echo=FALSE,
	             cache=TRUE,
               cache.path="cache/",
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

```{r}
library(FLBRP)
load("/home/laurie/Desktop/publications/swo-bio/data/swom.RData")
price(brp)=FLQuant(c(1,8,12,12,11,10,9,9,8,7,7),dimnames=list(age=0:10))*1000
units(price(brp))="Euro/Kg"

## costs
# per day
vcost=c("fuel"    =320,
        "bait"    =280,
        "salaries"=50,
        "others"  =30)
# per year
fcost(brp)[]=7080
units(fcost(brp))="Euro/year"

vcost(brp)[]=sum(vcost)
units(fcost(brp))="Euro/day"

vcost(brp)=vcost(brp)*58800/mean(fbar(swom)[,ac(2006:2010)]) #F/days

brp=brp(brp)

plot(brp)
```

```{r}
refpts(brp)
```

For the analysis, stock number at age estimates for the Mediterranean swordfish were used. The data were obtained from the latest ICCAT assessment (Anonymous 2008). In order to calculate the number of females at age a relationship between sex ratio and age was needed. An exponential relationship was estimated between sex-ratio and age, assuming that the sex ratio at age 3 is 0.5 and that sex-ratio at age 10 is 0.9 (unpublished data).  Thus the parameters of the relationship: sex ratio=a1*e^(age*b1) were estimated to be: a1=0.3887, b1=0.084. 
Consequently the number of females at age for the years 1985-2005 was estimated. At a subsequent step, a  fecundity of 0 was assumed for females of ages 0 to 2, a fecundity of 0.5 was assumed for females of age 3 and females of 4-years or higher ages were assumed to be fully fecund (fecundity=1) in order to calculate the number of fecund females at age (unpublished data). 


```{r}
par=FLPar(linf=238.59,k=0.185,t0=-1.404,a=8.90493e-7,b=3.554738,l50=142,
          fec= 7.01218E-03,fec2=3.994)

fec<-function(wt,par) 
  7.01218E-03*((wt/par["a"])^(1/par["b"]))^3.994 

brps=FLBRPs(SSB=brp,TEP=brp)

mat(brps[[2]])=fec(stock.wt(brps[[2]]),par)*mat(brps[[2]])/1e7
brps[[2]]=brp(brps[[2]])

plot(brps)
```

```{r}
refpts(brps[[1]])
refpts(brps[[2]])
```


